PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2021-12-01 main.tex
Add content

In figure \ref{fig:alpha_beta_mass}, we show the mass distribution of bodies from the final snapshot in each of the four cases. In addition to leaving fewer residual planetesimals, the large $\alpha$ simulations produce significantly larger embryos. Despite the vastly different encounter velocities of each population of bodies, the initial size of $\beta$ appears to have no significant effect on the final distribution of masses.

@@

Additionally, these results suggest that the value of $\alpha$, which is a function of only the initial conditions, controls the qualitative outcome of accretion. Across most of a planet-forming disk, $\alpha$ is small, and frequent gravitational encounters between the growing bodies will allow oligarchic growth to operate. At shorter orbital periods, however, the Hill sphere of a body is no longer mostly empty space, and it appears as if collisions play a more significant role. In this regime, we observe that runaway growth still commences, but nearly all of the planetesimals are swept up by the forming protoplanets, rather than being scattered onto higher eccentricity orbits, where they would otherwise remain as a remnant of the early stages of planet formation \citep{kokubo98, kokubo00}.

% Additional idea: run a simulation with an oligarch embedded in a disk of planetesimals for large and small alpha. Allow oligarch and planetesimals to collide. What does the eccentricity evolution of the oligarch look like in each case?
% See equation 32 from goldreich 2004: b_scat ~ sqrt(u/vh) R_H
% How does b_scat compare to particle size here?

@@

@@

@@

>>>>

In figure \ref{fig:alpha_beta_mass}, we show the mass distribution of bodies from the final snapshot in each of the four cases. In addition to leaving fewer residual planetesimals, the large $\alpha$ simulations produce significantly larger embryos. Despite the vastly different encounter velocities of each population of bodies, the initial size of $\beta$ (so long as bodies remain in the dispersion-dominated regime) appears to have no significant effect on the final distribution of masses.

@@

Additionally, these results suggest that the value of $\alpha$, which is a function of only the initial conditions, controls the qualitative outcome of accretion. Across most of a planet-forming disk, $\alpha$ is small, and frequent gravitational encounters between the growing bodies will allow oligarchic growth to operate. In the dispersion-dominated regime, close encounters drive the stirring between planetesimals and embryos \citep{weidenschilling89, ida90}. When $\alpha$ is large, the Hill sphere of a body is no longer mostly empty space, and close encounters that would otherwise result in stirring instead result in accretion. In this regime, we observe that runaway growth still commences, but nearly all of the planetesimals are swept up by the forming protoplanets, rather than being scattered onto higher eccentricity orbits, where they would otherwise remain as a remnant of the early stages of planet formation \citep{kokubo98, kokubo00}.

% Additional idea: run a simulation with an oligarch embedded in a disk of planetesimals for large and small alpha. Allow oligarch and planetesimals to collide. What does the eccentricity evolution of the oligarch look like in each case?

@@

% According to Ida 1990, 'distant encounters are not important' (but viscous stirring timescale can be described by Chandresehkar time). Also Weidenschilling 1989. This is also consistent with Goldreich 2004. So then why does the Armitage book describe viscous stirring in terms of distant encounters (b > b_min)?

% Wetherill + Stewart 1989, Ohtsuki 1990, Spaute 1991 find that runaway growth happens when velocity decreases with mass. Is that what we're seeing at high alpha?

@@

% Also mention that no eccentricity difference between large and small alpha regions, as we saw in the narrow annulus simulations

@@

% A mystery: what's so special about alpha = 0.1?
